The URL for our Team GitHub repository is https://github.com/stevenH721/Yaowen-Hu.git
The URL to the Kernel and Kaggle dataset is https://www.kaggle.com/jboysen/ny-home-mortgage
title: "Interim Report I"
output: word_document
---
```{r}
setwd("/Users/caiqingqing/Desktop")
hmda = read.csv("ny_hmda_2015.csv")
```
1. What is the data problem? What is the final managerial objective?



2. Describe the measurement types of each variable
Based on our observation and result from str function, we conclue the measurement types as follow.
Nominal: action_taken_name; agency_abbr; agency_name; applicant_ethnicity_name; applicant_race_name_1&2&3&4&5; applicant_sex_name; co_applicant_sex_name; country_name; denial_reason_name_1&2&3; edit_status_name; hoepa_status_name; lien_status_name; loan_purpose_name; msamd_name; owner_occupancy_name; preapproval_name; property_type_name; state_abbr; respondent_id

Ordinal: as_of_year

Interval: action_taken; agency_code; applicant_ethicity; applicant_race_1&2&3&4&5; applicant_sex; applicantion_date_indicatior; census_tract_number; co_applicant_ethnicity; co_applicant_race_1&2&3&4&5; co_applicant_sex; country_code; denial_reason_1&2&3; edit_status; hoepa_status; lien_status; loan_purpose; loan_type; msamd; owner_occupancy; preapproval; property_type; purchaser_type; sequence_number; state_code

Ratio: hud_median_family_income; loan_amount_000s; number_of_1_to_4_family_units; number_of_owner_occupied_units; minority_population; population; tate_spread; tract_to_msamd_income

3. Create a table summarizing the range or variation in each variable. Add statistics (mean,
median, standard deviation, etc.) as you deem necessary.
```{r}
library(dplyr)
## summary table for discrete variables
hmdadisc <- hmda %>%
  select(action_taken_name,agency_abbr,agency_name,applicant_ethnicity_name, applicant_race_name_1, applicant_race_name_2, applicant_race_name_3, applicant_race_name_4, applicant_race_name_5, applicant_sex_name, co_applicant_sex_name, county_name, denial_reason_name_1, denial_reason_name_2, denial_reason_name_3, edit_status_name, hoepa_status_name, lien_status_name, loan_purpose_name, msamd_name, owner_occupancy_name, preapproval_name, property_type_name, state_abbr)
summary(hmdadisc)

## summary table for continuous variables
hmdacon.df <- data.frame(matrix(NA, nrow = 43, ncol = 5))
hmdacon <- hmda%>%
  select(action_taken, agency_code, applicant_ethnicity, applicant_income_000s, applicant_race_1, applicant_race_2, applicant_race_3, applicant_race_4, applicant_race_name_5, applicant_sex,application_date_indicator, as_of_year, census_tract_number, co_applicant_ethnicity, co_applicant_race_1, co_applicant_race_2, co_applicant_race_3, co_applicant_race_4, co_applicant_race_5, co_applicant_sex,county_code, denial_reason_1, denial_reason_2, denial_reason_3, edit_status, hoepa_status, lien_status, loan_amount_000s, loan_purpose,loan_type, msamd, owner_occupancy, preapproval, property_type, purchaser_type, state_code, number_of_1_to_4_family_units, number_of_owner_occupied_units, hud_median_family_income, minority_population, population, rate_spread, tract_to_msamd_income)
na.omit(hmdacon)
summary(hmdacon)

## create a table
for(n in c(1:43)){
  hmdacon.df[n,1] = mean(hmdacon[[n]], na.rm = TRUE)
}

Mode = function(x){
  ux = sort(unique(x))
  tabx= table(x)
  maxf = ux[which(tabx == max(tabx))]
  return(maxf)
}

for(n in c(1:17)){
  hmdacon.df[n,2] = Mode(hmdacon[[n]])
}

for(n in c(19:43)){
  hmdacon.df[n,2] = Mode(hmdacon[[n]])
}
## As there is a speical variable which has two mode and can't simply run with loop, we calculate it seperatly
Mode(hmdacon[[18]])
hmdacon.df[18,2] = "4,5"

for(n in c(1:43)){
  hmdacon.df[n,3] = sd(hmdacon[[n]], na.rm =  TRUE)
}

for(n in c(1:43)){
  hmdacon.df[n,4] = median(hmdacon[[n]], na.rm = TRUE)
}

for(n in c(1:43)){
  hmdacon.df[n,5] = max(hmdacon[[n]], na.rm = TRUE) - min(hmdacon[[n]], na.rm = TRUE)
}

names(hmdacon.df) <- c("mean","mode","standard deviation","median","range")
```
4. How do you handle missing data in this dataset?
5. Provide histograms/density plots for key variables, such as action taken on loan, gender,
ethnicity, etc.
```{r}

```

6. Create bivariate frequency distributions (tables or plots) for key variables
```{r}

```

7. Discuss what the data patterns indicate, and what this could mean for the probability of
getting a loan approved.
```{r}

```




